---
title: "R Project 1 - Hello R"
author: "Ashle Markey"
date: "September 8, 2021"
output:
  html_document: default
  pdf_document: default
---

```{r, include=FALSE}
### Load packages
```
```{r load-packages, message=FALSE, echo=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1  
  - The datasaurus_dozen file has ***1846 rows*** and ***3 variables (columns)***
  - The variables included in the data frame are:
    + **dataset:** indicates which dataset the data are from
    + **x:** x-values 
    + **y:** y-values 

### Exercise 2

First we need to visualize this data to assess the form of the relationship between the variables `x` and `y`. We can do this by plotting the data in the dino dataset:  

```{r plot-dino, fig.height=3, fig.width=6, echo=FALSE}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
  
  Once we assess the visual relationship between the two variables, we can calculate the correlation between `x` and `y` in this dataset. When we do this, we get:

```{r cor-dino, echo=FALSE}
dino_data %>%
  summarize(r = cor(x, y))
```
*Calculating a correlation coefficient is not particularly needed for this case since the relationship between x and y is not linear.*


### Exercise 3
We need to visualize and asses the form of the relationship between the variables `x` and `y`. We can do this by plotting the data in the star dataset:  

```{r plot-star, fig.height=3, fig.width=6, echo=FALSE}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Once we assess the visual relationship between the two variables, we can calculate the correlation between `x` and `y` in this dataset. When we do this, we get:
 
```{r cor-star, echo=FALSE}
dino_data %>%
  summarize(r = cor(x, y))
```
  *The relationship between x and y variables are not linear.*  
  *When comparing the value of r in the star dataset to the value of r in the dino data set, you* 
  *will notice that the r value of star is -0.0630 where as the r value of dino is -0.0645. There*
  *is a -0.0015 difference between the two.*

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
